%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Mini Project} % Affiliation/role
{IDH (Indian Digital Herritage)} % Organization/group
{KLETU HUbli} % Location
{6th semester} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Classifies the given images into its substituent class(MultiClass)}
\item {Terms : Computer vision, Machine Learning, Neural networks, object recognition}
\item {Funded by government of India  (Archiological Department).}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Hobbie Project} % Affiliation/role
{DMaze} % Organization/group
{Hubli, Karnataka, India} % Location
{Sept. 2018 - PRESENT} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {DApp game written in solidity with frontend as unity}
\item {Terms : Blockchain, Etherium, Game development, Unity}
\item {Not yet deployed still in progress}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Course Project} % Affiliation/role
{Terrorist Activity Analysis} % Organization/group
{KLETU Hubli} % Location
{Jul. 2017 - Dec 2017} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Analysis of terrorist activity in India}
\item {Terms : Data mining, data analytics, pandas}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Member} % Affiliation/role
{PLUS (Laboratory for UNIX Security in POSTECH)} % Organization/group
{Pohang, S.Korea} % Location
{Sep. 2010 - Oct. 2011} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
\item {Participated on several hacking competition and won a good award.}
\item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
\item {Conducted penetration testing commissioned by national agency and corporation.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Member} % Affiliation/role
{MSSA (Management Strategy Club of POSTECH)} % Organization/group
{Pohang, S.Korea} % Location
{Sep. 2013 - PRESENT} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
\item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}